To Do List

### 2019-10-31 Papers.Rmd
Add Neural Network paper example

>>>>

- Neural network results reporting, figures: - `Deepimpute` - scRNA-seq imputation using deep neural networks. Sub-networks, each processes up to 512 genes needed to be imputed. Four layers: Input - dense (ReLU activation) - 20% dropout - output. MSE as loss function. Outperforms MAGIC, DrImpute, ScImpute, SAVER, VIPER, and DCA on multiple metrics (PCC, several clustering metrics). Using 9 datasets. https://github.com/lanagarmire/DeepImpute - Arisdakessian, Cédric, Olivier Poirion, Breck Yunits, Xun Zhu, and Lana X. Garmire. “DeepImpute: An Accurate, Fast, and Scalable Deep Neural Network Method to Impute Single-Cell RNA-Seq Data.” Genome Biology 20, no. 1 (December 2019): 211. https://doi.org/10.1186/s13059-019-1837-6.
